---
title: "Covid91 vaccine study Final2021"
author: "Jennifer Nava"
date: "August 6, 2021"
output: 
    html_document:
      number_sections: true
      toc: true
    
    
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
OldData <-read.csv(file="covid91.csv",header=TRUE)
#recode to remove the annoying "X" from the dataframe
FinalData <- OldData %>% mutate(infected = recode(infected, aids = "covid", none = "OK" )) %>% select(-one_of("X"))
FinalData <- FinalData %>%
mutate(across(where(is.character), as.factor))
FinalData$treatment <- relevel(FinalData$treatment,ref = "placebo")
#FinalData$infected <- relevel(FinalData$infected,ref= "OK")
guy = filter(FinalData, sex =="guy")
gal = filter(FinalData, sex =="gal")
gay = filter(FinalData, LGBTQ =="gay")
Druguser = filter(FinalData, DrugUser =="yes")
```



# Introduction

A new  preventative vaccine (covid91) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine. Structure your report in four sections each devoted to one of the four subgroups, use null and alternative hypothesis statements and correct statistical verbage when referencing p-values in conclusions.

```{r}
barchartGC(~infected + treatment, data=FinalData)
barchartGC(~infected + treatment,data=FinalData, type="percent")

```


 
```{r}
table1 <- xtabs(~treatment + infected, data=FinalData)
table2 <- xtabs(~infected + treatment,data=FinalData)
rowPerc(table1)
colPerc(table1)
```

# Guys Sex= "Guy"



### Plot barplots

#### Plot barplots tigerstats way

```{r}
barchartGC(~infected + treatment,data=FinalData)
barchartGC(~infected + treatment,data=FinalData, type="percent")

```

#### Plot barplots ggplot way

```{r}
dd2 <- gay %>% group_by(infected,treatment) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=infected,y=count,fill=treatment))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=infected,y=count,fill=treatment)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```
  
### Numerical Summaries  

```{r}
table1 <- xtabs(~infected + treatment, data=FinalData)
rowPerc(table1)
colPerc(table1)
```
## Inferential  

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```



# Gals Sex = "Gals"



# Sexual Orientation (LGBTQ = Gay)




# Drug Users "Drug Users = Yes"



